---
title: "PreProcess Moses"
output: html_document
---

```{r}
library(tidyverse)
```

# Method 1 (not used): Reads 40k ETCPoints line by line

```{r}
lines_moses <- read_lines("data_moses/ETCPoints_39381.m") %>%
  discard(~str_length(.x)==0)
```

```{r}
lines_moses %>% head
```

```{r}
df_moses <- tibble(line=lines_moses,
                   last_ch=line%>%str_sub(start=-1),
                   split=lines_moses %>% str_split(fixed("=")),
                   tokens=split %>% map_int(length)) %>%
  mutate(row=row_number(),.before=line)
```

```{r}
df_moses %>% count(tokens)
```

```{r}
df_moses %>% count(last_ch)
```

```{r}
df_moses %>% filter(last_ch!=";") %>% mutate(line_start=line %>% str_sub(end=40),
                                             line_end=line%>%str_sub(-40),.after=row) %>%
  select(row,last_ch,line_start,line_end)
```

```{r}
df_moses %>% filter(tokens==1) %>% mutate(line=line %>% str_trunc(50))
```


# Method 2: Read entire text file

```{r}
vec_moses <- read_file("data_moses/ETCPoints_39381.m")%>%
  str_split(fixed(";")) %>%
  first %>%
  str_squish
vec_moses %>% length
```

## Restrict to 1000 (first 1100) and clean

```{r}
vec_moses_clean <- vec_moses %>%
  head(1100) %>%
  str_remove_all("\\(\\*.+?\\*\\)") %>%
  str_replace_all(c("\\b([abc])\\^([2-8])\\b"="\\1\\2",
                    "\\b([Ss][ABC]?)\\^(2)\\b"="\\1\\2",
                    "Sqrt\\[([abc])\\]"="sqrt\\1",
                    "Sin\\[([ABC])\\]"="sin\\1",
                    "Cos\\[([ABC])\\]"="cos\\1",
                    "Tan\\[([ABC])\\]"="tan\\1",
                    "Cot\\[([ABC])\\]"="cot\\1",
                    "Sec\\[([ABC])\\]"="sec\\1",
                    "Csc\\[([ABC])\\]"="csc\\1",
                    "Cos\\[([ABC])/4\\]"="cosQuarter\\1",
                    "Sin\\[([ABC])/4\\]"="sinQuarter\\1",
                    "Sec\\[([ABC])/4\\]"="secQuarter\\1",
                    "Csc\\[([ABC])/4\\]"="cscQuarter\\1",
                    "Tan\\[([ABC])/4\\]"="tanQuarter\\1",
                    "Sin\\[([ABC])/3\\]"="sinThird\\1",
                    "Cos\\[([ABC])/3\\]"="cosThird\\1",
                    "Sec\\[([ABC])/3\\]"="secThird\\1",
                    "Csc\\[([ABC])/3\\]"="cscThird\\1",
                    "\\s*\\*\\s*"=" ")) %>%
  str_replace_all(fixed("\\[CapitalDelta]"),"area") %>%
  str_replace_all(fixed("\\[Tau]"),"phi") %>%
  str_replace_all(fixed("\\[Pi]"),"Pi") %>%
  str_replace_all(fixed("Sqrt[3]"),"sqrt3") %>%
  # x[848] weirndess
  str_replace_all(fixed("Cot[(2 a Pi)/(a+b+c)]"),"cotAp")
```

## Save cleaned file

```{r}
vec_moses_clean %>% write_lines("data_moses/vec_moses_1k_clean.txt")
```

# Last Phase: rotate literals

{"X(3)", Hold@{cosA, cosB, cosC}, "CIRCUMCENTER"},

a->b,b->c,c->a

TO DO:

- watch out, these are barycentrics
- remover o "x[...]=", need names
- use Mathematica to rotate all tokens and create expressions with Pow and separators

## convert .txt to .m

```{r}
df_moses_1k <- tibble(line=read_lines("data_moses/vec_moses_1k_clean.txt")) %>%
  mutate(tokens=str_split(line,"\\s*\\=\\s*"),
         token_count=map_int(tokens,length)) %>%
  mutate(row=row_number(),.before=line)
```

## Analyze tokens per line, all should be 2

```{r}
df_moses_1k %>% count(token_count)
```
Which ones are wrong

```{r}
df_moses_1k %>% filter(token_count!=2)
```
## token analysis

```{r}
reject_token <- function(tok_vec) {
  discard(tok_vec, ~str_length(.x)==0)
}
  
df_moses_1k_symbols <- df_moses_1k %>%
  #head(10) %>%
  # only valid ones
  filter(token_count==2) %>%
  # selects 2nd token
  mutate(lhs=map_chr(tokens,1),
         rhs=map_chr(tokens,2)) %>%
  mutate(symbols=str_split(rhs,"[^[:alnum:]]") %>% map(reject_token)) %>%
  filter(map_lgl(symbols,~length(.x)>0))
```

unnested symbols
```{r}
df_moses_1k_symbols_unnest <- df_moses_1k_symbols %>%
  select(symbols) %>%
  unnest(symbols)
```

Table of symbols

```{r}
df_moses_1k_symbols_unnest %>%
  count(symbols)
```

Save to file, to create substitute table

```{r}
df_moses_1k_symbols_unnest %>%
  count(symbols) %>%
  filter(!str_detect(symbols,"^\\d+$")) %>%
  pull(symbols) %>%
  write_lines("data_moses/symbols_1k.txt")
```

## Read rotation dictionary

note: perhaps rotation should be done w original barycentrics in mathematica first and then simplifying replacements should be done here.

```{r}
df_symbols_dict <- read_csv("data_moses/symbols_1k_rot_dict.txt")
```

Create replacement vector

```{r}
repl_symbols <- df_symbols_dict$to %>%
  set_names(df_symbols_dict$from %>% str_c("\\b",.,"\\b"))
```

Note: ρ's prevent overwriting

```{r}
repl_symbols %>% head(5)
```

```{r}
df_moses_1k_symbols_rotated <- df_moses_1k_symbols %>%
  #head(10) %>%
  select(lhs,rhs) %>%
  mutate(lhs=lhs%>%str_replace_all(c("\\s+"="","x"="X","\\["="(","\\]"=")"))) %>%
  mutate(rhs_1=str_replace_all(rhs,repl_symbols) %>%
           str_remove_all("ρ"),
         rhs_2=str_replace_all(rhs_1,repl_symbols) %>%
           str_remove_all("ρ"))
```

```{r}
df_moses_1k_symbols_rotated %>% head(1000) %>% tail
```


```{r}
df_moses_1k_symbols_rotated %>%
  #head %>%
  select(lhs) %>%
  mutate(xnum=str_sub(lhs,start=3)%>%
           str_sub(end=-2)%>%
           as.integer,.before=lhs) %>%
  mutate(xnum_diff=xnum-lag(xnum)) %>%
  filter(xnum_diff > 1)
```

{"X(3)", Hold@{cosA, cosB, cosC}, "CIRCUMCENTER"},

```{r}
df_moses_mathematica <- df_moses_1k_symbols_rotated %>%
  head(1000) %>%
  mutate(wolfram=str_c('{"',lhs,'", Hold@{',rhs,', ',rhs_1,', ',rhs_2,'}, "get_name"},')) %>%
  pull(wolfram) %>%
  str_c(collapse="\n") %>%
  # remove last comma
  str_sub(end=-2) %>%
  str_c("{\n",.,"\n}")
```


```{r}
df_moses_mathematica %>%
  write_file("data_moses/symbols_1k.m")
```

